Modern Graph Generators: A Survey

### 2018-10-07 main.tex
last pass on my side
Added affiliation

Author's addresses:
A. Bonifati, ...;
I. Holubov\'{a}, Department of Software Engineering, Faculty of Mathematics and Physics, Charles University, Malostransk\'{e} n\'{a}m. 25, 118 00 Praha~1, Czech Republic.
A. Prat-P\'erez, ...;
S. Sakr, ....
\end{bottomstuff}

>>>>

Author's addresses:
A. Bonifati, Universit\'{e} Claude Bernard Lyon 1, Liris CNRS Campus La
Doua 23-25 Avenue Pierre de Coubertin, 69622 Villerubanne, France;
I. Holubov\'{a}, Department of Software Engineering, Faculty of Mathematics and Physics, Charles University, Malostransk\'{e} n\'{a}m. 25, 118 00 Praha~1, Czech Republic.
  A. Prat-P\'erez, DAMA-UPC, Universitat Polit\`ecnica de Catalunya, Jordi Girona 1-3, 08034 Barcelona, Spain ;
S. Sakr, University of Tartu,J Liivi 2, Tartu 50409, Estonia.
\end{bottomstuff}
